Investigating The Fleishman Effect : Subjective Evaluations of Financial Satisfaction in the US General Social Survey

### 2023-03-13 outputs/paper/financial_satsifaction_in_us.qmd
changing file name to be more meaningful

Specifically, we retrieved the following demographic data as seen in @tbl-uss-demographic.

@@

For survey questions related to financial wellness, we retrieved the following data points as seen in @tbl-uss-financial

>>>>

Specifically, we retrieved the following demographic data described in @tbl-uss-demographic.

@@

For survey questions related to financial wellness, we retrieved the following data points described in @tbl-uss-financial.
